% !TEX program = xelatex
% This file is generated, don't manually edit!
\documentclass{resume}
\usepackage{lastpage}
\usepackage{fancyhdr}
\usepackage{linespacing_fix}
\usepackage[fallback]{xeCJK}
\renewcommand\headrulewidth{0pt}

\begin{document}

\name{roife}

\basicInfo{
  % \phone{(+86)} \textperiodcentered\
  \email{roifewu at gmail dot com} \textperiodcentered\
  \github[roife]{https://github.com/roife} \textperiodcentered\
  \homepage[roife.github.io]{https://roife.github.io}
}

\section{Education}
\educationentry{Beihang University (BUAA)}{Bachelor of \textit{Computer Science and Technology}}{2019.09 -- 2023.06}{
  GPA: 3.84/4.00
}

\section{Research Experience}
\researchEntry{A lightweight edge-side compiler for neural network operators}{BUAA}{2022.06 -- 2023.06}{
  \begin{itemize}
  \item Undergraduate thesis project, including independently implemented lightweight edge-side compiler and trimming work on the LLVM codegen module.
  \item Using shape information at the edge-side device to perform secondary optimization on offline compiled LLVM IR format neural network operators, to reduce the temporal and spatial overhead during operator runtime.
  \end{itemize}
}

\section{Projects}
\projectEntry{Ayame}{Java, ARMv7 | co-developer, implemented register allocation and codegen related optimizations}{https://github.com/No-SF-Work/ayame}{
  \begin{itemize}
    \item A SSA-based compiler for a subset of C, can export LLVM IR/ARMv7 ASM.
    \item Implement optimizations such as GVN, graph coloring register allocation, etc.
    \item Ranking 2nd in the Huawei Bisheng Cup 2021, performance exceeds \texttt{clang -O3} on nearly 1/3 of testcases.
  \end{itemize}
}

\projectEntry{Racoon}{Rust, LLVM IR}{https://github.com/roife/racoon}{
  \begin{itemize}
    \item A SysY to LLVM IR compiler implemented in Rust.
    \item The reference implementation in Rust for labs of BUAA SE Compiler Design course.
  \end{itemize}
}

\projectEntry{Hanggai}{SwiftUI, Vue, Rails | co-developer, participated in iOS app and web backend development}{https://github.com/Caniformia}{
  \begin{itemize}
    \item An app for the course \textit{Introduction to Aeronautics and Astronautics} in BUAA, supporting the web and iOS.
    \item \textit{Hanggai} can be downloaded from AppStore.
  \end{itemize}
}

\section{Honors \& Awards}
\scholarshipEntry{National Scholarship}{Top 1.5\%}{2022.09}
\scholarshipEntry{NSCSCC Compilation System Design Competition (Huawei Bisheng Cup)}{the First Price, ranking 2nd}{2021.08}

\section{Skills}
\begin{itemize}
\entry{Programming Languages}{
    C, C++, Java, Rust, Swift, Python, JavaScript, Ruby, Verilog(SV), Haskell
  }
\entry{Tech Stack}{
    Vue, Rails, Django, SwiftUI | Docker, PostgreSQL, Redis, CI, Git
  }
\entry{Compilers}{
    Familiar with LLVM IR and LLVM;
    understand prevalent SSA-based optimization algorithms
  }
\entry{PL Theory}{
    Familiar with functional programming languages;
    understand type theory;
  }
\entry{Dev Tools}{
    macOS, Linux | Emacs, Xcode, JetBrains IDEs
  }
\end{itemize}

\section{Others}
\begin{itemize}
\entry{Teacher assistants} {
    \begin{itemize}
    \datedEntry{Programming in Practice}{BUAA}{2020.09 - 2021.02}
      {Design course assignments \& tutor students}
    \datedEntry{Object oriented Design and Construction}{BUAA, S.T.A.R team}{2021.09 - 2022.06}
      {Maintain course systems \& design labs and tests \& tutor students}
    \end{itemize}
  }
\entry{Blog}{
    \url{https://roife.github.io}
  }
\entry{Languages}{
    Mandarin Chinese (native), English (CET-6)
  }
\end{itemize}

\end{document}
